---
title: "Teachers Attitudes Towards Democracy Education as a Function of Their Values"
subtitle: "Reproducible Documentation of Analysis"
author: "Samuel Merk, Nikolas Hübner, Gabriel Nagy"
format:
  html: 
    theme:
      light: flatly
      dark: darkly
toc: true
---

# Data Wrangling
## Libraries
```{r}
#| label: loading the libraries
#| results: 'hide'
#| message: FALSE
#| warning: FALSE

library(modelsummary)
library(hrbrthemes)
library(haven)
library(reactable)
library(brms)
library(patchwork)
library(skimr)
library(MplusAutomation)
library(ggrepel)
library(ggdensity)
library(knitr)
library(geomtextpath)
library(sjPlot)
library(sjlabelled)
library(occupar)
library(tidyverse)
```


## Data Import
###  Data german teachers
```{r}
#| label: import german teacher data
#| message: false

data <- read_spss("data/data_forsa_inservice_teachers_raw.sav")%>% 
  mutate(across(c(f1_1, f1_2, f1_3, f1_4, f1_5, f1_6, f1_7, f1_8, f1_9, f1_10,
                  f1_11, f1_12, f1_13, f1_14, f1_15, f1_16), function(x) ifelse(x == 7, NA, 7 - as.numeric(x)))) %>% 
  mutate(across(c(msb_1, msb_2, mst_1, mst_2, mhe_1, mhe_2, mle_1, mle_2, 
                  mma_1, mma_2, msi_1, msi_2, mtr_1, mtr_2, mko_1, mko_2, 
                  mbe_1, mbe_2, muv_1, muv_2, muv_3), function(x) ifelse(x == 7, NA, x))) %>% 
  mutate(across(c(msb_1, msb_2, mst_1, mst_2, mhe_1, mhe_2, mle_1, mle_2, 
                  mma_1, mma_2, msi_1, msi_2, mtr_1, mtr_2, mko_1, mko_2, 
                  mbe_1, mbe_2, muv_1, muv_2, muv_3), function(x) 7 - as.numeric(x))) |> 
  
  mutate(
   PID = 1:n(),
   msd = rowMeans(across(c(msb_1, msb_2)), na.rm = T),
   mst = rowMeans(across(c(mst_1, mst_2)), na.rm = T),
   mhe = rowMeans(across(c(mhe_1, mhe_2)), na.rm = T),
   mac = rowMeans(across(c(mle_1, mle_2)), na.rm = T),
   mpo = rowMeans(across(c(mma_1, mma_2)), na.rm = T),
   mse = rowMeans(across(c(msi_1, msi_2)), na.rm = T),
   mtr = rowMeans(across(c(mtr_1, mtr_2)), na.rm = T),
   mco = rowMeans(across(c(mko_1, mko_2)), na.rm = T),
   mbe = rowMeans(across(c(mbe_1, mbe_2)), na.rm = T),
   mun = rowMeans(across(c(muv_1, muv_2, muv_3)), na.rm = T),
   `Self-Direction` = msd, 
   Stimulation = mst, 
   Hedonism = mhe, 
   Achievement = mac, 
   Power = mpo, 
   Security = mse, 
   Tradition = mtr, 
   Conformity = mco, 
   Benevolence = mbe, 
   Universalism = mun,
   isco08 = case_when(sc2 == 1 ~ "2341", # primary school
                      sc2 == 2 ~ "2330", # Hauptschule
                      sc2 == 3 ~ "2330", # Realschule
                      sc2 == 4 ~ "2330", # Comprehensive School  
                      sc2 == 5 ~ "2330", # Gymnasium
                      sc2 == 6 ~ "2352", # Special Education
                      sc2 == 7 ~ "2350" # Other
                      ),
   sex = as.factor(ges), # 1 = male, 2 = female
   agekat = ordered(altkat), # 1 = < 25, 2 = 35-44, 3 = 45-50, 4 = 50 < 
   isei = occupar::isco08toISEI08(isco08),
   teacher = "yes",
   teacher = factor(teacher, levels = c("no", "yes")),
   teacher_num = ifelse(teacher == "yes", 1, 0),
   teacher_num_factor = as.factor(teacher_num),
   cntry = "DE",
   eisced = ordered(7, levels = c(1,2,3,4,5,6,7)),
   `Democracy Education` = f1_1,
   `Practising tolerance` =  f1_5,
   `Social compentencies` =  f1_3,
   `Independent action` =  f1_7,
   `Preparation for future life` =  f1_11,
   `Recognition of cultural diversity` =  f1_16,
   `Commitment to peace` =  f1_14,
   `Personal development` =  f1_2,
   `Responsibility for the environment` =  f1_4,
   `Respecting human rights` =  f1_6,
   `Recognition of basic social values` =  f1_10,
   `Equality between the genders` =  f1_15,
   `Orientation towards achievement` =  f1_8,
   `Promotion of a sense of home` =  f1_9,
   `Promotion of independent learning` =  f1_12,
   `Peaceful handling of conflicts` =  f1_13,
   `Years Teaching` = case_when(sc3 == 1 ~ "less than 5 years",
                                sc3 == 2 ~ "5-9 years",
                                sc3 == 3 ~ "10-19 years",
                                sc3 == 4 ~ "20-29 years",
                                sc3 == 5 ~ "more than 30 years",
                                sc3 == 6 ~ NA),
   Sex = ifelse(sex == 2, "female", "male"),
   `School Type` = case_when(sc2 == 1 ~ "Primary School", 
                             sc2 == 2 ~ "Lower Track Secondary School", 
                             sc2 == 3 ~ "Middle Track Secondary School", 
                             sc2 == 4 ~ "Comprehensive School", 
                             sc2 == 5 ~ "Academic Track Secondary School", 
                             sc2 == 6 ~ "Special Education", 
                             sc2 == 7 ~ "Other",
                             sc2 == 8 ~ NA),
   `Federal State` = case_when(buland == 1 ~ "Schleswig-Holstein",
                               buland == 2 ~ "Hamburg",
                               buland == 3 ~ "Lower Saxony",
                               buland == 4 ~ "Bremen",
                               buland == 5 ~ "North Rhine-Westphalia",
                               buland == 6 ~ "Hessen",
                               buland == 7 ~ "Rhineland-Palatinate",
                               buland == 8 ~ "Baden-Württemberg",
                               buland == 9 ~ "Bavaria",
                               buland == 10 ~ "Saarland",
                               buland == 11 ~ "Berlin",
                               buland == 12 ~ "Brandenburg",
                               buland == 13 ~ "Mecklenburg-Western Pomerania",
                               buland == 14 ~ "Saxony",
                               buland == 15 ~ "Saxony-Anhalt",
                               buland == 16 ~ "Thuringia"),
   Age = case_when(altkat == 1 ~ "<35",
                   altkat == 2 ~ "35-44",
                   altkat == 3 ~ "45-50",
                   altkat == 4 ~ "50+"))

write_csv(data, 
          "Dashboard/data/data.csv")

```




## Data skim
```{r}
#| label: skimming data

data |> 
  skimr::skim()
```

## Covariates 


# The structure of human values
## Perfect circumplex model
```{r}
#| label: mplus code perfect circumplex

model_perfect_circumplex <- 
'lmsd by msd*0.8;
 lmst by mst*0.8;
 lmhe by mhe*0.8;
 lmac by mac*0.8;
 lmpo by mpo*0.8;
 lmse by mse*0.8;
 lmtr by mtr*0.8;
 lmco by mco*0.8;
 lmbe by mbe*0.8;
 lmun by mun*0.8;
 msd-mun*0.5;
 lmsd-lmun@0;
 
 gen by lmsd-lmun@1;

 cos1 by lmsd@1.0;
 cos1 by lmst* 0.99 (c1_02);
 cos1 by lmhe* 0.97 (c1_03);
 cos1 by lmac* 0.58 (c1_04);
 cos1 by lmpo* 0.44 (c1_05);
 cos1 by lmse*-0.17 (c1_06);
 cos1 by lmtr*-0.32 (c1_07);
 cos1 by lmco*-0.28 (c1_08);
 cos1 by lmbe* 0.29 (c1_09);
 cos1 by lmun* 0.91 (c1_10);

 sin1 by lmsd@0.0;
 sin1 by lmst*-0.13 (s1_02);
 sin1 by lmhe* 0.26 (s1_03);
 sin1 by lmac* 0.82 (s1_04);
 sin1 by lmpo* 0.90 (s1_05);
 sin1 by lmse* 0.99 (s1_06);
 sin1 by lmtr* 0.95 (s1_07);
 sin1 by lmco* 0.96 (s1_08);
 sin1 by lmbe* 0.96 (s1_09);
 sin1 by lmun*-0.42 (s1_10);

 gen*0.1 (b0);
 cos1*0.5 (b1);
 sin1*0.5 (b1);

 gen-sin1 with gen-sin1@0;'
  

constraint_perfect_circumplex <- 
'b0 > 0;
 b1 > 0;
 
 b0 = 1 - b1;
 
 c1_02 = cos(0.6283185);  s1_02 = sin(0.6283185);
 c1_03 = cos(1.2566371);  s1_03 = sin(1.2566371);
 c1_04 = cos(1.8849556);  s1_04 = sin(1.8849556);
 c1_05 = cos(2.5132741);  s1_05 = sin(2.5132741);
 c1_06 = cos(3.1415927);  s1_06 = sin(3.1415927);
 c1_07 = cos(3.7699112);  s1_07 = sin(3.7699112);
 c1_08 = cos(4.3982297);  s1_08 = sin(4.3982297);
 c1_09 = cos(5.0265482);  s1_09 = sin(5.0265482);
 c1_10 = cos(5.6548668);  s1_10 = sin(5.6548668);'
```


```{r}
#| label: run perfect circumplex
#| cache: false

# Define the MPlus Model
perfect_circumplex_mod <- 
  mplusObject(
  TITLE = 'Perf.-Circ.;',
  MODEL = model_perfect_circumplex,
  MODELCONSTRAINT = constraint_perfect_circumplex,
  rdata = data %>% 
    select(msd, mst, mhe, mac, mpo, mse, mtr, mco, mbe, mun))

# Run Model in Mplus
perfect_circumplex_fit <- 
  mplusModeler(perfect_circumplex_mod,
             modelout = "MPlus_Files/perfect_circumplex.inp",
             run = TRUE, quiet = FALSE, hashfilename = F)

# Store fit indices
fit_perfect_circumplex <-
  tibble(
    CFI = perfect_circumplex_fit$results$summaries$CFI,
    SRMR = perfect_circumplex_fit$results$summaries$SRMR,
    RMSEA_Estimate = perfect_circumplex_fit$results$summaries$RMSEA_Estimate,
    ChiSqM_Value = perfect_circumplex_fit$results$summaries$ChiSqM_Value,
    ChiSqM_DF = perfect_circumplex_fit$results$summaries$ChiSqM_DF
  )

```


### Model Result
```{r}
#| label: fit perfect circumplex
fit_perfect_circumplex %>%
  kable(.)
```


## Quasi-Circumplex model (Cosine function model)
```{r}
#| label: mplus code componentes quasi circumplex
model_quasi_circumplex <- 
'lmsd by msd*0.8;
 lmst by mst*0.8;
 lmhe by mhe*0.8;
 lmac by mac*0.8;
 lmpo by mpo*0.8;
 lmse by mse*0.8;
 lmtr by mtr*0.8;
 lmco by mco*0.8;
 lmbe by mbe*0.8;
 lmun by mun*0.8;
 msd-mun*0.5;
 lmsd-lmun@0;
 
 gen by lmsd-lmun@1;

 cos1 by lmsd@1.0;
 cos1 by lmst* 0.99 (c1_02);
 cos1 by lmhe* 0.97 (c1_03);
 cos1 by lmac* 0.58 (c1_04);
 cos1 by lmpo* 0.44 (c1_05);
 cos1 by lmse*-0.17 (c1_06);
 cos1 by lmtr*-0.32 (c1_07);
 cos1 by lmco*-0.28 (c1_08);
 cos1 by lmbe* 0.29 (c1_09);
 cos1 by lmun* 0.91 (c1_10);

 sin1 by lmsd@0.0;
 sin1 by lmst*-0.13 (s1_02);
 sin1 by lmhe* 0.26 (s1_03);
 sin1 by lmac* 0.82 (s1_04);
 sin1 by lmpo* 0.90 (s1_05);
 sin1 by lmse* 0.99 (s1_06);
 sin1 by lmtr* 0.95 (s1_07);
 sin1 by lmco* 0.96 (s1_08);
 sin1 by lmbe* 0.96 (s1_09);
 sin1 by lmun*-0.42 (s1_10);

 gen*0.1 (b0);
 cos1*0.5 (b1);
 sin1*0.5 (b1);

 gen-sin1 with gen-sin1@0;'

constraint_quasi_circumplex <- 
'b0 > 0;
 b1 > 0;
 
 b0 = 1 - b1;

 new(tst*0.58);
 new(the*0.42);
 new(tac*1.61);
 new(tpo*1.89);
 new(tse*3.66);
 new(ttr*3.97);
 new(tco*3.46);
 new(tbe*5.08);
 new(tun*5.04);
 
 c1_02 = cos(tst);  s1_02 = sin(tst);
 c1_03 = cos(the);  s1_03 = sin(the);
 c1_04 = cos(tac);  s1_04 = sin(tac);
 c1_05 = cos(tpo);  s1_05 = sin(tpo);
 c1_06 = cos(tse);  s1_06 = sin(tse);
 c1_07 = cos(ttr);  s1_07 = sin(ttr);
 c1_08 = cos(tco);  s1_08 = sin(tco);
 c1_09 = cos(tbe);  s1_09 = sin(tbe);
 c1_10 = cos(tun);  s1_10 = sin(tun);'
```


```{r}
#| label: quasi circumplex
#| cache: false

quasi_circumplex_mod <- 
  mplusObject(
  TITLE = 'Quasi-Circ.',
  MODEL = model_quasi_circumplex,
  MODELCONSTRAINT = constraint_quasi_circumplex, 
  OUTPUT = 'samp tech1 sval;',
  rdata = data %>% 
    select(msd, mst, mhe, mac, mpo, mse, mtr, mco, mbe, mun))

# Run Model in Mplus
quasi_circumplex_fit <- 
  mplusModeler(quasi_circumplex_mod,
             modelout = "MPlus_Files/quasi_circumplex.inp",
             run = TRUE, quiet = FALSE, hashfilename = F)

# Store fit indices and theta 
fit_quasi_circumplex <-
  tibble(
    CFI = quasi_circumplex_fit$results$summaries$CFI,
    SRMR = quasi_circumplex_fit$results$summaries$SRMR,
    RMSEA_Estimate = quasi_circumplex_fit$results$summaries$RMSEA_Estimate,
    ChiSqM_Value = quasi_circumplex_fit$results$summaries$ChiSqM_Value,
    ChiSqM_DF = quasi_circumplex_fit$results$summaries$ChiSqM_DF
  )

thetas_quasi_circumplex <-
  quasi_circumplex_fit$results$parameters$unstandardized %>%
  as_tibble() %>%
  filter(paramHeader == "New.Additional.Parameters") %>%
  add_row(param = "TSD", est = 0) %>%
  mutate(theta = est %% (2 * pi),
         theta_grad = theta * 180 / pi)
```

### Model Result
```{r}
#| label: print fit quasi circumplex
fit_quasi_circumplex %>% 
  kable(.)
```

As the angular positions are the following
```{r} 
#| label: depict quasi circumplex, 
#| echo: false
#| fig-width: 5.8
thetas_quasi_circumplex %>% 
  arrange(theta_grad) |> 
  ggplot(aes(x = 1, 
                y = theta_grad, 
                group = param)) +
  geom_label_repel(aes(label = param)) + 
  geom_point(aes(color = param)) + 
  # geom_textpath(data = tibble(x = c(0,1),
  #                             y = c(38.1, 38.1),
  #                             text = "Stimulation"),
  #               aes(x = x, y = y, label = text)) +
  scale_x_continuous(breaks = c(), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(), limits = c(0, 360)) +
  coord_polar(theta = "y", 
              direction = -1, 
              clip = "off",
              start = 1/8*pi) + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        panel.grid  = element_blank(),
        legend.position = "none") +
  theme_minimal() + 
  xlab("") + 
  ylab("")
```


## Quasi-Circumplex model with 2 Fourier Components 
```{r}
#| label: mplus code componentes quasi circumplex 2F
model_quasi_circumplex2F <- 
'lmsd by msd*0.8;
 lmst by mst*0.8;
 lmhe by mhe*0.8;
 lmac by mac*0.8;
 lmpo by mpo*0.8;
 lmse by mse*0.8;
 lmtr by mtr*0.8;
 lmco by mco*0.8;
 lmbe by mbe*0.8;
 lmun by mun*0.8;

 msd-mun*0.5;

 lmsd-lmun@0 ;

 gen by lmsd-lmun@1;

 cos1 by lmsd@1.0;
 cos1 by lmst* 0.99 (c1_02);
 cos1 by lmhe* 0.97 (c1_03);
 cos1 by lmac* 0.58 (c1_04);
 cos1 by lmpo* 0.44 (c1_05);
 cos1 by lmse*-0.17 (c1_06);
 cos1 by lmtr*-0.32 (c1_07);
 cos1 by lmco*-0.28 (c1_08);
 cos1 by lmbe* 0.29 (c1_09);
 cos1 by lmun* 0.91 (c1_10);

 sin1 by lmsd@0.0;
 sin1 by lmst*-0.13 (s1_02);
 sin1 by lmhe* 0.26 (s1_03);
 sin1 by lmac* 0.82 (s1_04);
 sin1 by lmpo* 0.90 (s1_05);
 sin1 by lmse* 0.99 (s1_06);
 sin1 by lmtr* 0.95 (s1_07);
 sin1 by lmco* 0.96 (s1_08);
 sin1 by lmbe* 0.96 (s1_09);
 sin1 by lmun*-0.42 (s1_10);

 cos2 by lmsd@1.0;
 cos2 by lmst* 0.97 (c2_02);
 cos2 by lmhe* 0.87 (c2_03);
 cos2 by lmac*-0.34 (c2_04);
 cos2 by lmpo*-0.61 (c2_05);
 cos2 by lmse*-0.95 (c2_06);
 cos2 by lmtr*-0.80 (c2_07);
 cos2 by lmco*-0.84 (c2_08);
 cos2 by lmbe*-0.84 (c2_09);
 cos2 by lmun* 0.65 (c2_10);

 sin2 by lmsd@0.0;
 sin2 by lmst*-0.25 (s2_02);
 sin2 by lmhe* 0.50 (s2_03);
 sin2 by lmac* 0.94 (s2_04);
 sin2 by lmpo* 0.79 (s2_05);
 sin2 by lmse*-0.33 (s2_06);
 sin2 by lmtr*-0.60 (s2_07);
 sin2 by lmco*-0.54 (s2_08);
 sin2 by lmbe* 0.55 (s2_09);
 sin2 by lmun*-0.76 (s2_10);



 gen*0.1 (b0);
 cos1*0.5 (b1);
 sin1*0.5 (b1);
 cos2*0.1 (b2);
 sin2*0.1 (b2);

 gen-sin2 with gen-sin2@0;'

constraint_quasi_circumplex2F <- 
'b0 > 0;
b1 > 0;
b2 > 0;

b0 = 1 - (b1 + b2);

new(t_02*6.88779);
new(t_03*0.95236);
new(t_04*2.07423);
new(t_05*2.14695);
new(t_06*3.30459);
new(t_07*3.62782);
new(t_08*3.23085);
new(t_09*4.77318);
new(t_10*5.37742);

c1_02 = cos(t_02);  s1_02 = sin(t_02);
c1_03 = cos(t_03);  s1_03 = sin(t_03);
c1_04 = cos(t_04);  s1_04 = sin(t_04);
c1_05 = cos(t_05);  s1_05 = sin(t_05);
c1_06 = cos(t_06);  s1_06 = sin(t_06);
c1_07 = cos(t_07);  s1_07 = sin(t_07);
c1_08 = cos(t_08);  s1_08 = sin(t_08);
c1_09 = cos(t_09);  s1_09 = sin(t_09);
c1_10 = cos(t_10);  s1_10 = sin(t_10);


c2_02 = cos(2*t_02);  s2_02 = sin(2*t_02);
c2_03 = cos(2*t_03);  s2_03 = sin(2*t_03);
c2_04 = cos(2*t_04);  s2_04 = sin(2*t_04);
c2_05 = cos(2*t_05);  s2_05 = sin(2*t_05);
c2_06 = cos(2*t_06);  s2_06 = sin(2*t_06);
c2_07 = cos(2*t_07);  s2_07 = sin(2*t_07);
c2_08 = cos(2*t_08);  s2_08 = sin(2*t_08);
c2_09 = cos(2*t_09);  s2_09 = sin(2*t_09);
c2_10 = cos(2*t_10);  s2_10 = sin(2*t_10);'
```


```{r}
#| label: quasi circumplex 2F
#| cache: false

quasi_circumplex2F_mod <- 
  mplusObject(
  TITLE = 'Quasi-Circ. 2F',
  MODEL = model_quasi_circumplex2F,
  MODELCONSTRAINT = constraint_quasi_circumplex2F, 
  OUTPUT = 'samp tech1 sval;',
  rdata = data %>% 
    select(msd, mst, mhe, mac, mpo, mse, mtr, mco, mbe, mun))

# Run Model in Mplus
quasi_circumplex2F_fit <- 
  mplusModeler(quasi_circumplex2F_mod,
             modelout = "MPlus_Files/quasi_circumplex2F.inp",
             run = TRUE, quiet = FALSE, hashfilename = F)

# Store fit indices and theta 
fit_quasi_circumplex2F <-
  tibble(
    CFI = quasi_circumplex2F_fit$results$summaries$CFI,
    SRMR = quasi_circumplex2F_fit$results$summaries$SRMR,
    RMSEA_Estimate = quasi_circumplex2F_fit$results$summaries$RMSEA_Estimate,
    ChiSqM_Value = quasi_circumplex2F_fit$results$summaries$ChiSqM_Value,
    ChiSqM_DF = quasi_circumplex2F_fit$results$summaries$ChiSqM_DF
  )

thetas_quasi_circumplex2F <-
  quasi_circumplex2F_fit$results$parameters$unstandardized %>%
  as_tibble() %>%
  filter(paramHeader == "New.Additional.Parameters") %>%
  add_row(param = "TSD", est = 0) %>%
  mutate(theta = est %% (2 * pi),
         theta_grad = theta * 180 / pi)
```

### Model Result
```{r}
#| label: print fit quasi circumplex 2F
fit_quasi_circumplex2F %>% 
  kable(.)
```

As the angular positions are the following
```{r} 
#| label: depict quasi circumplex 2F, 
#| echo: false
#| fig-width: 5.8
thetas_quasi_circumplex2F %>% 
  arrange(theta_grad) |> 
  ggplot(aes(x = 1, 
                y = theta_grad, 
                group = param)) +
  geom_label_repel(aes(label = param)) + 
  geom_point(aes(color = param)) + 
  # geom_textpath(data = tibble(x = c(0,1),
  #                             y = c(38.1, 38.1),
  #                             text = "Stimulation"),
  #               aes(x = x, y = y, label = text)) +
  scale_x_continuous(breaks = c(), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(), limits = c(0, 360)) +
  coord_polar(theta = "y", 
              direction = -1, 
              clip = "off",
              start = 1/8*pi) + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        panel.grid  = element_blank(),
        legend.position = "none") +
  theme_minimal() + 
  xlab("") + 
  ylab("")
```


# Integrating Democracy Education into the value circumplex
```{r}
#| label: mplus code SPMCE democracy education quasi circumplex 2F
#| 
model_spmce_de_quasi_circumplex2F <- 
           'lmsd by msd*0.49515;
            lmst by mst*0.80853;
            lmhe by mhe*0.63985;
            lmac by mac*0.61272;
            lmpo by mpo*0.75586;
            lmse by mse*0.79618;
            lmtr by mtr*0.60242;
            lmco by mco*0.79836;
            lmbe by mbe*0.46238;
            lmun by mun*0.37573;

            rmsd by lmsd*1.328 (u01);
            rmst by lmst*0.855 (u02);
            rmhe by lmhe*1.303 (u03);
            rmac by lmac*1.381 (u04);
            rmpo by lmpo*0.613 (u05);
            rmse by lmse*0.941 (u06);
            rmtr by lmtr*1.320 (u07);
            rmco by lmco*1.007 (u08);
            rmbe by lmbe*0.915 (u09);
            rmun by lmun*1.312 (u10);

            lmsd-lmun@0;
            rmsd-rmun@1;
            rmsd-rmun with rmsd-rmun@0;

            msd-mun@0;


            lev by lmsd-lmun*0.59 (b0);

            cos1 by lmsd* 0.760 (b1);
            cos1 by lmst* 0.626 (c1_02);
            cos1 by lmhe* 0.441 (c1_03);
            cos1 by lmac*-0.367 (c1_04);
            cos1 by lmpo*-0.414 (c1_05);
            cos1 by lmse*-0.750 (c1_06);
            cos1 by lmtr*-0.672 (c1_07);
            cos1 by lmco*-0.758 (c1_08);
            cos1 by lmbe* 0.046 (c1_09);
            cos1 by lmun* 0.469 (c1_10);

            sin1 by lmsd@ 0.000;
            sin1 by lmst* 0.432 (s1_02);
            sin1 by lmhe* 0.620 (s1_03);
            sin1 by lmac* 0.666 (s1_04);
            sin1 by lmpo* 0.638 (s1_05);
            sin1 by lmse*-0.123 (s1_06);
            sin1 by lmtr*-0.355 (s1_07);
            sin1 by lmco*-0.068 (s1_08);
            sin1 by lmbe*-0.759 (s1_09);
            sin1 by lmun*-0.598 (s1_10);

            cos2 by lmsd* 0.280 (b2);
            cos2 by lmst* 0.100 (c2_02);
            cos2 by lmhe*-0.093 (c2_03);
            cos2 by lmac*-0.152 (c2_04);
            cos2 by lmpo*-0.115 (c2_05);
            cos2 by lmse* 0.269 (c2_06);
            cos2 by lmtr* 0.160 (c2_07);
            cos2 by lmco* 0.279 (c2_08);
            cos2 by lmbe*-0.282 (c2_09);
            cos2 by lmun*-0.068 (c2_10);

            sin2 by lmsd@0.0;
            sin2 by lmst* 0.266 (s2_02);
            sin2 by lmhe* 0.268 (s2_03);
            sin2 by lmac*-0.240 (s2_04);
            sin2 by lmpo*-0.259 (s2_05);
            sin2 by lmse* 0.091 (s2_06);
            sin2 by lmtr* 0.235 (s2_07);
            sin2 by lmco* 0.050 (s2_08);
            sin2 by lmbe*-0.034 (s2_09);
            sin2 by lmun*-0.276 (s2_10);

            lev-sin2@1 ;

            lev-sin2 with lev-sin2@0;
            lev-sin2 with rmsd-rmun@0;

            !extension

            ly by f1_1*1;
            f1_1@0;
            ly@1;

            lev  WITH ly* 0.12467 (r10);
            cos1 WITH ly* 0.03016 (rc1);
            sin1 WITH ly*-0.23793 (rs1);
            cos2 WITH ly*-0.08606 (rc2);
            sin2 WITH ly*-0.02217 (rs2);


            ly with rmsd* 0.00126  (ru01);
            ly with rmst* 0.00290  (ru02);
            ly with rmhe*-0.00019  (ru03);
            ly with rmac* 0.01425  (ru04);
            ly with rmpo*-0.04127  (ru05);
            ly with rmse* 0.01500  (ru06);
            ly with rmtr* 0.01200  (ru07);
            ly with rmco* 0.04851  (ru08);
            ly with rmbe*-0.07711  (ru09);
            ly with rmun* 0.08375  (ru10);'

constraint_spmce_de_quasi_circumplex2F <- 
           '0 = 1 - sqrt(b0**2 + b1**2 + b2**2);
            
            b0 > 0;
            b1 > 0;
            b2 > 0;
            
            new(tst*6.88777);
            new(the*0.95234);
            new(tac*2.07419);
            new(tpo*2.14695);
            new(tse*3.30457);
            new(ttr*3.62782);
            new(tco*3.23080);
            new(tbe*4.77319);
            new(tun*5.37745);
            
            c1_02 = b1*cos(tst);  s1_02 = b1*sin(tst);
            c1_03 = b1*cos(the);  s1_03 = b1*sin(the);
            c1_04 = b1*cos(tac);  s1_04 = b1*sin(tac);
            c1_05 = b1*cos(tpo);  s1_05 = b1*sin(tpo);
            c1_06 = b1*cos(tse);  s1_06 = b1*sin(tse);
            c1_07 = b1*cos(ttr);  s1_07 = b1*sin(ttr);
            c1_08 = b1*cos(tco);  s1_08 = b1*sin(tco);
            c1_09 = b1*cos(tbe);  s1_09 = b1*sin(tbe);
            c1_10 = b1*cos(tun);  s1_10 = b1*sin(tun);
            
            
            c2_02 = b2*cos(2*tst);  s2_02 = b2*sin(2*tst);
            c2_03 = b2*cos(2*the);  s2_03 = b2*sin(2*the);
            c2_04 = b2*cos(2*tac);  s2_04 = b2*sin(2*tac);
            c2_05 = b2*cos(2*tpo);  s2_05 = b2*sin(2*tpo);
            c2_06 = b2*cos(2*tse);  s2_06 = b2*sin(2*tse);
            c2_07 = b2*cos(2*ttr);  s2_07 = b2*sin(2*ttr);
            c2_08 = b2*cos(2*tco);  s2_08 = b2*sin(2*tco);
            c2_09 = b2*cos(2*tbe);  s2_09 = b2*sin(2*tbe);
            c2_10 = b2*cos(2*tun);  s2_10 = b2*sin(2*tun);
            
            ! Extension
            
            new(g0*0.217);
            new(ga*0.313);
            new(da*4.838);
            
            r10 = g0*b0;
            rc1 = ga*b1*cos(1*da);
            rs1 = ga*b1*sin(1*da);
            rc2 = ga*b2*cos(2*da);
            rs2 = ga*b2*sin(2*da);
            
            
            0 = 
            (b0*ru01)/u01+(b0*ru02)/u02+(b0*ru03)/u03+(b0*ru04)/u04+(b0*ru05)/u05+
            (b0*ru06)/u06+(b0*ru07)/u07+(b0*ru08)/u08+(b0*ru09)/u09+(b0*ru10)/u10;
            
            0 = 
            ((b1**2*cos(1*(0  -da))+b2**2*cos(2*(0  -da)))*ru01)/u01+
            ((b1**2*cos(1*(tst-da))+b2**2*cos(2*(tst-da)))*ru02)/u02+
            ((b1**2*cos(1*(the-da))+b2**2*cos(2*(the-da)))*ru03)/u03+
            ((b1**2*cos(1*(tac-da))+b2**2*cos(2*(tac-da)))*ru04)/u04+
            ((b1**2*cos(1*(tpo-da))+b2**2*cos(2*(tpo-da)))*ru05)/u05+
            ((b1**2*cos(1*(tse-da))+b2**2*cos(2*(tse-da)))*ru06)/u06+
            ((b1**2*cos(1*(ttr-da))+b2**2*cos(2*(ttr-da)))*ru07)/u07+
            ((b1**2*cos(1*(tco-da))+b2**2*cos(2*(tco-da)))*ru08)/u08+
            ((b1**2*cos(1*(tbe-da))+b2**2*cos(2*(tbe-da)))*ru09)/u09+
            ((b1**2*cos(1*(tun-da))+b2**2*cos(2*(tun-da)))*ru10)/u10;
            
            0 = 
            ((b1**2*sin(1*(da-0  ))+2*b2**2*sin(2*(da-0  )))*ru01)/u01+
            ((b1**2*sin(1*(da-tst))+2*b2**2*sin(2*(da-tst)))*ru02)/u02+
            ((b1**2*sin(1*(da-the))+2*b2**2*sin(2*(da-the)))*ru03)/u03+
            ((b1**2*sin(1*(da-tac))+2*b2**2*sin(2*(da-tac)))*ru04)/u04+
            ((b1**2*sin(1*(da-tpo))+2*b2**2*sin(2*(da-tpo)))*ru05)/u05+
            ((b1**2*sin(1*(da-tse))+2*b2**2*sin(2*(da-tse)))*ru06)/u06+
            ((b1**2*sin(1*(da-ttr))+2*b2**2*sin(2*(da-ttr)))*ru07)/u07+
            ((b1**2*sin(1*(da-tco))+2*b2**2*sin(2*(da-tco)))*ru08)/u08+
            ((b1**2*sin(1*(da-tbe))+2*b2**2*sin(2*(da-tbe)))*ru09)/u09+
            ((b1**2*sin(1*(da-tun))+2*b2**2*sin(2*(da-tun)))*ru10)/u10;'
```


```{r}
#| label: SPMCE DE circumplex 2F
#| cache: false

spmce_de_quasi_circumplex2F_mod <- 
  mplusObject(
  TITLE = 'SPMCE Democracy Ed Quasi-Circ. 2F',
  MODEL = model_spmce_de_quasi_circumplex2F,
  MODELCONSTRAINT = constraint_spmce_de_quasi_circumplex2F, 
  OUTPUT = 'samp tech1 sval;',
  rdata = data %>% 
    select(msd, mst, mhe, mac, mpo, mse, mtr, mco, mbe, mun, f1_1))

# Run Model in Mplus
spmce_de_quasi_circumplex2F_fit <- 
  mplusModeler(spmce_de_quasi_circumplex2F_mod,
             modelout = "MPlus_Files/spmce_de_quasi_circumplex2F.inp",
             run = TRUE, quiet = FALSE, hashfilename = F)

# Store fit indices and theta 
fit_spmce_de_quasi_circumplex2F <-
  tibble(
    CFI = spmce_de_quasi_circumplex2F_fit$results$summaries$CFI,
    SRMR = spmce_de_quasi_circumplex2F_fit$results$summaries$SRMR,
    RMSEA_Estimate = spmce_de_quasi_circumplex2F_fit$results$summaries$RMSEA_Estimate,
    ChiSqM_Value = spmce_de_quasi_circumplex2F_fit$results$summaries$ChiSqM_Value,
    ChiSqM_DF = spmce_de_quasi_circumplex2F_fit$results$summaries$ChiSqM_DF
  )

thetas_spmce_de_quasi_circumplex2F <-
  spmce_de_quasi_circumplex2F_fit$results$parameters$unstandardized %>%
  as_tibble() %>%
  filter(paramHeader == "New.Additional.Parameters") %>%
  add_row(param = "TSD", est = 0) %>%
  mutate(theta = est %% (2 * pi),
         theta_grad = theta * 180 / pi)
```

### Model Result
```{r}
#| label: print fit spmce quasi circumplex 2F
fit_spmce_de_quasi_circumplex2F %>% 
  kable(.)
```

As the angular positions are the following
```{r} 
#| label: depict spmce quasi circumplex (rotated)
#| echo: false
#| fig-width: 5.8
thetas_spmce_de_quasi_circumplex2F %>% 
  arrange(theta_grad) |> 
  filter(!param %in% c("G0", "GA")) %>% 
  mutate(x = ifelse(param == "DA", .3, 1)) %>% 
  ggplot(aes(x = x, 
             y = theta_grad, 
             group = param)) +
  geom_label_repel(aes(label = param)) + 
  geom_point(aes(color = param)) + 
  # geom_textpath(data = tibble(x = c(0,1),
  #                             y = c(38.1, 38.1),
  #                             text = "Stimulation"),
  #               aes(x = x, y = y, label = text)) +
  scale_x_continuous(breaks = c(), limits = c(0, 1)) +
  scale_y_continuous(breaks = c(), limits = c(0, 360)) +
  coord_polar(theta = "y", 
              direction = -1, 
              clip = "off",
              start = 0) + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        panel.grid  = element_blank(),
        legend.position = "none") +
  theme_minimal() + 
  xlab("") + 
  ylab("")
```





